Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex
rewrite of grads

\textbf{Value function learning}
We use DDPG to learn the action value function.
DDPG learns both a policy and a value function but we do not use the policy.
In our experiments, we parameterised both the actor and critic as MLPs with two hidden layers of width $128$ with ELU activations.
We train them using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a batch size of $512$.
DDPG uses a target value function to stabilise learning and for the soft target updates
we used $\tau = 0.005$. \todo{What is $\tau$ ?}
DDPG is an off-policy algorithm where the exploration policy samples from a noise process, which here was a Gaussian distribution with $\sigma=0.1$ and clipping at $0.3$.

>>>>

\textbf{Value function learning}
We use DDPG to learn the action value function.
DDPG learns both a policy and a value function but we do not use the policy.
In our experiments, we parameterised both the actor and critic as MLPs with two hidden layers of width $128$ with ELU activations.
We train them using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a batch size of $512$.
DDPG uses a target value function to stabilise learning and for the soft target updates
we used $\tau = 0.005$. 
DDPG is an off-policy algorithm where the exploration policy samples from a noise process, which here was a Gaussian distribution with $\sigma=0.1$ and clipping at $0.3$.
